Blowship - Untraceable Instantaneous Message Transfer via a Central Server

### 2014-03-14 paper.tex
Thing

\subsection{Basic Protocol}
Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity. This could be done using a public keyserver of some kind, or perhaps they have exchanged keys in advance through some other channel. Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge.

Alice can then send a message to Bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow B$ by sending the following message to Surge: 
\\
Let $M = E_{KRA}[  time || nonce || message ]$
\\Let $F_{ij}[x] = E_{KUi}[ ID_j || E_{KUj}[ x ] ]$
\\
Alice sends: $F_{S1}[F_{S2}[...F_{nB}[ M ]]]$ to Surge.

@@

If we assume that The Fort has not been established (no peers are colluding with Surge), then Alice only needs to choose $n = log(N)$ to remain anonymous from Surge. If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = 2^{log(n)} = N$ possible messages that Alice sent, and some $< N$ possible destinations. The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n = N$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose. If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$. Then, the size of Alice's anonymity probability distribution is $\approx 1$ since the sender probabilities are roughly uniform.

In this way Surge gains no information about the sender of the message. If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance less than $n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, and $S = - \frac{1}{4} log(\frac{1}{2N})$ which is still reasonable, though Alice could compensate further by randomly choosing the length of her circuit.

@@

Let $\phi$ be the proportion of peers who are colluding with Surge. Then $s = \phi N$ peers are part of The Fort, and on average $(1 - \phi)n$ of $n$ chosen peers still help maintain privacy, leading to the expectation $E[P_{AB}] = 2^{-(1 - \phi) log(N)}$.

@@

Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability $\sum\limits_{i=x}^n\phi^i$ where 
\\ $P_{AB} = 2^{-(n - x)} = 2^{-(log(N) - x)} = \gamma$
\\ $ \Rightarrow x = 2^{loglog(N)/\gamma}$

>>>>

\subsection{Basic Protocol}
Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity. This could be done using a public keyserver of some kind, or perhaps they have exchanged keys in advance through some other channel. Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge. (This can be done using private information retrieval)

Alice can then send a message to Bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow P_2 \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow S \rightarrow B$ by sending the following message to Surge: 
\\
Let \scriptsize$M = ID_A||E_{KRA}[ header || time || nonce || message ]$
\normalsize
\\Let \scriptsize$F_{ij}[x] = header||E_{KUi}[ ID_j || E_{KUj}[ x ] ]$
\normalsize
\\
Alice sends: $F_{S1}[F_{S2}[...F_{nB}[ M ]]]$ to Surge.

@@

If we assume that The Fort has not been established (no peers are colluding with Surge), then Alice only needs to choose $n = \log(N)$ to remain anonymous from Surge. If every node sends 2 messages at once, and her message passes through $\log(N)$ nodes, then there are $2^n = 2^{\log(n)} = N$ possible messages that Alice sent, and some $< N$ possible destinations. The likelihood is that in $\log(N)$ steps from Alice, there will be less than $2^n = N$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose. If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = \log_z(N)$ and then $z^{\log_z(N)} = N$. Then, the size of Alice's anonymity probability distribution is $\approx 1$ since the sender probabilities are roughly uniform.

In this way Surge gains no information about the sender of the message. If Surge knows Alice will choose $n = \log(N)$, then he can rule out any peer in the chain with distance less than $n$ from Alice, and then $P_{AB} = 2^{-(\log(N)-1)} = 2/N$, and $S = - \frac{1}{4} \log(\frac{1}{2N})$ which is still reasonable, though Alice could compensate further by randomly choosing the length of her circuit.

@@

Let $\phi$ be the proportion of peers who are colluding with Surge. Then $s = \phi N$ peers are part of The Fort, and on average $(1 - \phi)n$ of $n$ chosen peers still help maintain privacy, leading to the expectation $E[P_{AB}] = 2^{-(1 - \phi) \log(N)}$.

@@

Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability $\sum\limits_{i=x}^n\phi^ifdas$ where 
\\ $P_{AB} = 2^{-(n - x)} = 2^{-(\log(N) - x)} = \gamma$
\\ $ \Rightarrow x = 2^{\log\log(N)/\gamma}$
